%-------------------------
% Resume in Latex
% Author : AMAR NATH VAID
% Website: https://github.com/anv2amar/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{ragged2e}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-8pt}}
  }
}

\newcommand{\newItem}[2]{
  \item\small{
    \textbf{#1}{\hfill#2}
  }
}

\newcommand{\resumeSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5}\\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\projectSubheading}[3]{
  \item\small{
    \textbf{#1}\textit{: #2}\textit{\hfill#3}
  }
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-10pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-8pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-10pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\huge Amar Nath Vaid}} & 3415 Perkins Ln W, Seattle, WA 98199\\
  \href{https://anv2amar.github.io}{anv2amar.github.io} & Email : \href{mailto:anv2amar@gmail.com}{anv2amar@gmail.com}\\
 &  Mobile : +1 (929)-381-9654 \\
\end{tabular*}\vspace{-16pt}

 %-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \projectSubheading
      {Amazon, Seattle, WA, U.S.}{Software Development Engineer}{03/04/2019 - Present}
      \resumeItemListStart
          \justifying{\item Working in the Elastic Block Store team in AWS responsible for storing data in EBS volumes over cloud and taking in-time snapshots of the stored data to create incremental backups and enabling customers to perform different read/write operations on them.}
          \justifying{\item Created new EBS Direct APIs to support business and made optimizations in existing an existing API to reduce it's memory footprint by 20\%.}
          \justifying{\item To improve the team's testing process, I implemented a canary workflow to mimic actual customer traffic with an incremental tps for stress and load testing. This enabled the team to troubleshoot issues with half of the initially required SDE efforts.}
          \justifying{\item Worked on securing AWS Backup Service Control Plane. Migrated APIs under our services to an enhanced and more secure credentials management system. My design incorporated short lived credentials, which reduced the blast radius of any potential security threat by 70\%.}
      \resumeItemListEnd
      
    \projectSubheading
      {Amazon, San Jose, CA, U.S.}{Software Development Engineering Intern}{09/10/2018 - 11/31/2018}
      \resumeItemListStart
          \justifying{\item Worked as a part of the Hardware Monitoring Team responsible for building and maintaining the set of software used to monitor hardware issues and failures in AWS servers.}
          \justifying{\item Implemented dirty reboot analyzer - a tool that monitors AWS Servers to look out for reboots marked as 'dirty'. The tool analyzes the system reboots to get to the root cause based on ingested System Event Logs and Machine Check Exceptions from the AWS Servers. Log root cause and related data in a redshift database ready to be ingested by other sources for various purposes.}
      \resumeItemListEnd
    
    \projectSubheading
      {DKOP Labs Pvt. Ltd., India}{Software Engineer Intern}{04/15/2015 - 07/15/2015}
      \resumeItemListStart
          \justifying{\item Designed digital circuits using logic gates and ICs by carrying out simulation of the digital circuits using and C, Python and Verilog. Implemented the I2C communication protocol for data transfer between master-slave devices.}   
      \resumeItemListEnd

    \projectSubheading
      {UvSofts Tech Pvt. Ltd., India}{Summer Intern}{04/10/2014 - 07/02/2014}
      \resumeItemListStart
    {\item Developed a DTMF controlled security system using an AVR microcontroller. Programming for the embedded circuit was done in C language.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
%

%--------PROGRAMMING SKILLS------------
\section{Skills and Expertise}
   {\textbf{Languages:} Java, Python, C\#, Ruby, C, C++ ; \textbf{Web:} SQL, JavaScript, HTML, CSS, PHP}\vspace{-8pt}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Florida}{Gainesville, FL}
      {Master of Science in Computer Science;  GPA: 3.44}{01/01/2017 -- 12/20/2018}
      {\textbf{Coursework:} Algorithms, Advanced Data Structures, Object Oriented Programming}
    \resumeSubheading
      {Thapar Institute of Engineering and Technology}{Patiala, India}
      {Bachelor of Engineering in Electronics and Communication;  GPA: 7.12/10.0}{08/01/2013 -- 07/15/2017}
      {}\vspace{-10pt}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Academic Projects}

\resumeSubHeadingListStart
 \projectSubheading
      {MIPS Simulator}{Java}{2018}
\justifying{\linebreak Implemented and designed a Petri Net simulator for MIPS Processor in Java to produce a disassembled output and a simulation trace for given line of instructions in machine language. Registers and data memory values were printed equivalent to input code.}\vspace{-5pt}
    \projectSubheading
      {Care for her}{Unity 3D, C\#, Virtual Reality}{2018}
\justifying{\linebreak A mobile application to spread awareness of maternity care and issues during puberty that educated the users of the causes, treatment and symptoms of common maternity problems and problems faced at the time of attaining puberty. The application lets users learn in an interactive way with the help of Virtual Reality. Development was done in Unity 3D. Actions and interactive behaviors to application elements were scripted in MonoDevelop using C\#. 3D models were extracted from Turbosquid and Autodesk.}\vspace{-5pt}
\projectSubheading
      {Carter}{SQL, HTML, CSS, JavaScript, JSP}{2018}
\justifying{\linebreak A web application to buy and sell used cars. A large database for the used cars was obtained from eBay. A buyer could browse through the advertisements posted by other sellers and obtain the results conforming to his/her requirements by applying various available filters which would use complex SQL
queries to extract the desired tuples from the database. A platform for efficient communication between a buyer and seller was developed.}\vspace{-5pt}
     \projectSubheading
      {FurnitureAR}{Android Application, Augmented Reality, Unity 3D, C\#}{2017}
\justifying{\linebreak An application to display three-dimensional visualizations of home furnishing products which augments them in the real environment using marker-based augmented reality. Application was developed using Unity 3D and scripting was done using C\#.}\vspace{-5pt}
    \projectSubheading
      {Dynamic de Bruijn graphs for genome assembly}{C++}{2017}
\justifying{\linebreak An application to display three-dimensional visualizations of home furnishing products which augments them in the real environment using marker-based augmented reality. Application was developed using Unity 3D and scripting was done using C\#.}\vspace{-5pt}
	\projectSubheading
      {Huffman Encoder-Decoder}{Java}{2017}
\justifying{\linebreak Using Huffman Coding and implementing 4-way cache optimized heap to encode and decode large data.}\vspace{-5pt}

%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\section{Involvements}\vspace{0pt}

\begin{itemize}[leftmargin=*]
  \justifying{\item \small Received award for best Organizing Committee President, \textit{\textbf{AIESEC India}}}\vspace{-5pt}{\small{\textit{\hfill 2015}}}
  \justifying{\item Design and Marketing head of \textbf{\textit{Thapar University Model United Nations}}}{\small{\textit{\hfill2016}}}
   \end{itemize}




%-------------------------------------------
\end{document}
